A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-21 sections/Overview.tex
Clarify the freshness condition

\jimmy{TODO: Mention the implicit freshness conditions in the premises throughout the text}

@@

>>>>

@@

\jimmy{Mention the implicit freshness conditions in the premises throughout the text}
Please note that when we introduce a new binder in the premise, we implicitly pick a fresh one.
This applies to rules such as $\mathtt{wf_d\forall}$, $\mathtt{wf_dabs}$, $\mathtt{{\le}\forall R}$,
throughout the whole text.
For algorithmic rules in Figure~\ref{fig:alg}, the right-hand side $\Gm'$
is actually the premise if re-written in bit-step style.
